Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-06-06 LaTeX/supplemental_rev.tex
manuscript changes for revisions.

% cross-referencing appendices
\usepackage{xr}
\externaldocument{skewt-rev}

% \usepackage[left=1in,top=1in,right=1in]{geometry}
% \pdfpageheight 11in
% \pdfpagewidth 8.5in
% \linespread{2.0}
\input{mycommands.sty}

@@

% \appendix
\renewcommand{\thesection}{Web Appendix \Alph{section}}
% \renewcommand{\tablename}{Web Table}
% \renewcommand{\figurename}{Web Figure}
% \renewcommand{\thetable}{Web Table \arabic{table}}

\section{MCMC details} \label{a:mcmc}
The MCMC sampling for the model in Section \ref{s:hier} is done using {\tt R} (http://www.r-project.org). Whenever possible, we select conjugate priors (see Appendix \ref{a:posterior}); however, for some of the parameters, no conjugate prior distributions exist.
For these parameters, we use a random walk Metropolis-Hastings update step.
In each Metropolis-Hastings update, we tune the algorithm during the burn-in period to give acceptance rates near 0.40.

\subsection*{Spatial knot locations}
For each day, we update the spatial knot locations, $\bw_1, \ldots, \bw_K$, using a Metropolis-Hastings block update.
Because the spatial domain is bounded, we generate candidate knots using the transformed knots $\bw^*_1, \ldots, \bw^*_K$ (see section \ref{s:temporal}) and a random walk bivariate Gaussian candidate distribution
\begin{align*}
	{\bw^*_k}^{(c)} \sim \text{N}({\bw^*_k}^{(r - 1)}, s^2 I_2)
\end{align*}
where ${\bw^*_k}^{(r - 1)}$ is the location for the transformed knot at MCMC iteration $r - 1$, $s$ is a tuning parameter, and $I_2$ is an identity matrix.
After candidates have been generated for all $K$ knots, the acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[ Y_t(\bs | \bw_1^{(c)}, \ldots, \bw_K^{(c)}, \ldots)] }{l[ Y_t(\bs | \bw_1^{(r - 1)}, \ldots, \bw_K^{(r - 1)}, \ldots)]} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K}\phi(\bw_k^{(c)})}{ \prod_{k = 1}^{K}\phi(\bw_k^{(r - 1)})} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K} p({\bw^*_k}^{(c)})}{ \prod_{k = 1}^{K} p({\bw^*_k}^{(r - 1)})}\right\}
\end{align*}
where $l$ is the likelihood given in (\ref{eq:hier}), and $p(\cdot)$ is the prior either taken from the time series given in (\ref{s:temporal}) or assumed to be uniform over $\calD$.
The candidate knots are accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial random effects}
If there is no temporal dependence amongst the observations, we use a Gibbs update for $z_{tk}$, and the posterior distribution is given in \ref{a:posterior}.
If there is temporal dependence amongst the observations, then we update $z_{tk}$ using a Metropolis-Hastings update.
Because this model uses $|z_{tk}|$, we generate candidate random effects using the $z^*_{tk}$ (see Section \ref{s:temporal}) and a random walk Gaussian candidate distribution
\begin{align*}
  {z^*_{tk}}^{(c)} \sim \text{N}({z^*_{tk}}^{(r - 1)}, s^2)
\end{align*}
where ${z^*_{tk}}^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
The acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[Y_t(\bs) | z_{tk}^{(c)}, \ldots] }{ l[Y_t(\bs) | z_{tk}^{(r - 1)}]} \right\} \times \left\{ \frac{ p[ z_{tk}^{(c)} ] }{ p[ z_{tk}^{(r - 1)}]}\right\}
\end{align*}
where $p[\cdot]$ is the prior taken from the time series given in Section \ref{s:temporal}.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Variance terms}
When there is more than one site in a partition, then we update $\sigma^2_{tk}$ using a Metropolis-Hastings update.
First, we generate a candidate for $\sigma^2_{tk}$ using an IG$(a^*/s, b^*/s)$ candidate distribution in an independence Metropolis-Hastings update where $a^* = (n_{tk} + 1) / 2 + a$, $b^* = [Y_{tk}^T \Sigma^{-1}_{tk} Y_{tk} + z_{tk}^2] / 2 + b$, $n_{tk}$ is the number of sites in partition $k$ on day $t$, and $Y_{tk}$ and $\Sigma^{-1}_{tk}$ are the observations and precision matrix for partition $k$ on day $t$.
The acceptance ratio is
\begin{align*}
  R = \left\{
    \frac{ l[Y_t(\bs) | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[Y_t(\bs) | {\sigma^2_{tk}}^{(r - 1)}]}
    \right\} \times \left\{
    \frac{ l[z_{tk} | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[z_{tk} | {\sigma^2_{tk}}^{(r - 1)}, \ldots] }
    \right\} \times \left\{
    \frac{ p[ {\sigma^2_{tk}}^{(c)} ] }
         { p[ {\sigma^2_{tk}}^{(r - 1)}] }
    \right\} \times \left\{
    \frac{ c[ {\sigma^2_{tk}}^{(r - 1)}] }
         { c[ {\sigma^2_{tk}}^{(c)}]}
    \right\}
\end{align*}
where $p[\cdot]$ is the prior either taken from the time series given in Section \ref{s:temporal} or assumed to be IG$(a, b)$, and $c[\cdot]$ is the candidate distribution.
The candidate is accepted with probability $\min\{R, 1\}$.

@@

\section{Posterior distributions} \label{a:posterior}

\subsection*{Conditional posterior of $z_{tk} \mid \ldots $}\label{s:mvcondu}
If knots are independent over days, then the conditional posterior distribution of $|z_{tk}|$ is conjugate.
For simplicity, drop the subscript $t$, let $\tilde{z}_{tk} = |z_{tk}|$, and define
\begin{align*}
R(\bs) = \left\{
    \begin{array}{ll}
        Y(\bs) - X(\bs) \beta &s \in P_l\\[1em]
        Y(\bs) - X(\bs) \beta - \lambda \tilde{z}(\bs) \qquad & s \notin P_l
    \end{array}
\right.
\end{align*}
Let
\begin{align*}
    R_1 &= \text{the vector of } R(\bs) \text{ for } s \in P_l \\
    R_2 &= \text{the vector of } R(\bs) \text{ for } s \notin P_l \\
    \Omega &= \Sigma^{-1}.
\end{align*}
Then
\begin{align*}
    \pi(z_l | \ldots) &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)^T
        \left( \begin{array}{cc}
            \Omega_{11} & \Omega_{12}\\
            \Omega_{21} & \Omega_{22}
        \end{array} \right)
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)
        +  \frac{ {\tilde{z}_l}^2 }{ \sigma_l^2 }\right]
    \right\} I(z_l > 0) \\
        &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \Lambda_l {\tilde{z}_l}^2 - 2 \mu_l \tilde{z}_l \right] \right\}
\end{align*}
where
\begin{align*}
    \mu_l &= \lambda ( R_1^T \Omega_{11} + R_2^T \Omega_{21} )\bOne\\
    \Lambda_l &= \lambda^2 \bOne^T \Omega_{11} \bOne + \frac{ 1 }{ \sigma^2_l }.
\end{align*}
Then $\tilde{Z}_l | \ldots \sim N_{(0, \infty)} (\Lambda_l^{-1} \mu_l, \Lambda_l^{-1})$

\subsection*{Conditional posterior of $\beta \mid \ldots$}\label{s:betapost}
Let $\beta \sim \mbox{N}_{p}(0, \Lambda_0)$ where $\Lambda_0$ is a precision matrix. Then
\begin{align*}
    \pi(\beta \mid \ldots) & \propto \exp \left\{ - \frac{ 1 }{ 2 } \beta^T \Lambda_0 \beta - \frac{ 1 }{ 2 } \sum_{t = 1 }^T [\bY_t - X_t \beta - \lambda |z_t|]^T \Omega [\bY_t - X_t \beta - \lambda |z_t|] \right\}\\
     & \propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \beta^T \Lambda_\beta \beta  - 2 \sum_{ t = 1 }^T [ \beta^T X_t^T \Omega (\bY_t - \lambda |z_t| )] \right] \right\}\\
     & \propto \mbox{N} ( \Lambda_\beta^{-1} \mu_\beta , \Lambda_\beta^{-1})
\end{align*}
where
\begin{align*}
    \mu_\beta &= \sum_{t=1}^{T} \left[ X_t^T \Omega (\bY_t - \lambda |z_t|) \right]\\
    \Lambda_\beta &= \Lambda_0 + \sum_{ t = 1 }^{ T} X_t^T \Omega X_t.
\end{align*}

\subsection*{Conditional posterior of $\sigma^2 \mid \ldots$}\label{s:sigpost}
In the case where $L = 1$ and temporal dependence is negligible, then $\sigma^2$ has a conjugate posterior distribution.
Let $\sigma_t^2 \iid \mbox{IG}(\alpha_0, \beta_0)$. For simplicity, drop the subscript $t$. Then
\begin{align*}
    \pi(\sigma^2 \mid \ldots) & \propto (\sigma^2)^{ -\alpha_0 - 1 / 2 - n / 2 - 1} \exp \left\{ -\frac{\beta_0}{\sigma^2} - \frac{ |z|^2 }{2 \sigma^2} - \frac{ (\bY - \bmu)^T \Sigma^{-1} (\bY - \bmu) }{2 \sigma^2} \right\} \\
    & \propto (\sigma^2)^{ -\alpha_0 - 1 / 2 - n / 2 - 1} \exp \left\{ - \frac{ 1 }{ \sigma^2 } \left[\beta_0 + \frac{ |z|^2 }{ 2 } + \frac{ 1 }{ 2 } (\bY - \bmu)^T \Sigma^{-1} (\bY - \mu) \right] \right\} \\
    & \propto \mbox{IG} (\alpha^*, \beta^*)
\end{align*}
where
\begin{align*}
    \alpha^* &= \alpha_0 + \frac{1}{2} + \frac{n}{2} \\
    \beta^* &= \beta_0 + \frac{ |z|^2 }{ 2 } + \frac{ 1 }{ 2 }(\bY - \bmu)^T \Sigma^{-1} (\bY - \bmu).
\end{align*}
In the case that $L > 1$, a random walk Metropolis Hastings step will be used to update $\sigma^2_{lt}$.

\subsection*{Conditional posterior of $\lambda \mid \ldots$}\label{s:lambdapost}
For convergence purposes we model $\lambda = \lambda_1 \lambda_2$ where
\begin{align}
  \lambda_1 &= \left\{ \begin{array}{ll}
      +1 \quad & \text{w.p.} 0.5\\
      -1 \quad & \text{w.p.} 0.5
   \end{array}\right.\\
   \lambda^2_2 & \sim IG(\alpha_\lambda, \beta_\lambda).\\
\end{align}
Then
\begin{align*}
  \pi(\lambda_2 \mid \ldots) &\propto {\lambda_2^2}^{(-\alpha_\lambda - 1)} \exp\left\{ - \frac{ \beta_\lambda }{ \lambda_2^2} \right\} \prod_{t = 1}^{T} \prod_{k = 1}^K \frac{1} {\lambda_2} \exp\left\{ - \frac{ z^2_{tk} }{ 2 \lambda_2^2  \sigma_{tk})^2} \right\} \\
   & \propto {\lambda_2^2}^{(-\alpha_\lambda - kt - 1)} \exp \left\{ -\frac{1}{\lambda^2_2} \left[ \beta_\lambda + \frac{ z^2 }{2 \sigma^2_{tk}} \right] \right\}
\end{align*}
Then $\lambda_2 \mid \ldots \sim IG \left(\alpha_\lambda + kt, \beta_\lambda + \frac{ z^2 }{2 \sigma^2_{tk}} \right)$

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{a:proofsamepartition}
Let $c$ be the midpoint of $\bs_1$ and $\bs_2$.
Define $A$ as the circle centered at $c$ with radius $h / 2$ where $h = ||\bs_1 - \bs_2||$ is the distance between sites $\bs_1$ and $\bs_2$.
Consider a homogeneous spatial Poisson process over $A$ with intensity given by
\begin{align*}
  \mu(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PPA}^* h^2.
\end{align*}
Consider a partition of $A$ into four regions, $B_1$, $B_2$, $R_1$, $R_2$ as seen in Web Figure \ref{fig:hpp}.
\begin{figure}
  \includegraphics[width=\linewidth]{plots/circles}
  \caption{Illustration of the partition of $A$.}
  \label{fig:hpp}
\end{figure}
Let $N_j$ be the number of knots in $B_j, j = 1, 2$.
Then
\begin{align}
  P(\bs_1 \in P_i, \bs_2 \in P_{j \neq i}) \ge P(N_1 > 0, N_2 > 0)
\end{align}
since knots in both $B_1$ and $B_2$ is sufficient, but not necessary, to ensure that $\bs_1$ and $\bs_2$ are in different partition sets.
By definition of a Poission process, $N_1$ and $N_2$ are independent and thus $P(N_1 > 0, N_2 > 0) = P(N_1 > 0)^2$, and the intensity measure over $B_1$ is given by
\begin{align}
  \mu(B_1) &= \lambda_{PP} |B_1| = \lambda_{PP} \frac{h^2}{4} \left(\frac{2 \pi}{3} - \frac{\sqrt{3}}{2} \right) \nonumber \\
       &= \lambda^*_{PPB1} h^2.
\end{align}
So,
\begin{align}
  P(\bs_1 \in P_i, \bs_2 \in P_{j \neq i}) >= P(N_1 > 0)^2 = [1 - P(N_1 = 0)]^2 = [1 - \exp\left(-\lambda^*_{PPB1} h^2\right)]^2
\end{align}
which goes to 1 as $h$ goes to infinity.

@@

\section{Skew-$t$ distribution} \label{a:skewt}
\subsection*{Univariate skew-$t$ distribution}
We say that $Y$ follows a univariate extended skew-$t$ distribution with location $\xi \in \calR$, scale $\omega > 0$, skew parameter $\alpha \in \calR$, and degrees of freedom $\nu$ if has distribution function
\begin{align}
  f_{\text{EST}}(y) = 2 f_T (z; \nu) F_T\left[ \alpha z \sqrt{ \frac{ \nu + 1 }{ \nu + z^2}}; \nu + 1 \right]
\end{align}
where $f_T(t; \nu)$ is a univariate Student's $t$ with $\nu$ degrees of freedom, $F_T(t; \nu) = P(T < t)$, and \hbox{$z = (y - \xi) / \omega$}.

\subsection*{Multivariate skew-$t$ distribution}
If $\bZ \sim \text{ST}_d(0, \bar{\bOmega}, \balpha, \eta)$ is a $d$-dimensional skew-$t$ distribution, and $\bY = \xi + \bomega \bZ$, where $\bomega = \text{diag}(\omega_1, \ldots, \omega_d)$, then the density of $Y$ at $y$ is
\begin{align}
  f_y(\by) = det(\bomega)^{-1} f_z(\bz)
\end{align}
where
\begin{align}
  f_z(\bz) &= 2 t_d(\bz; \bar{\bOmega}, \eta) T \left[ \balpha^T \bz \sqrt{ \frac{\eta + d}{\nu + Q(\bz)} }; \eta + d\right] \\
  \bz &= \bomega^{-1}(\by - \xi)
\end{align}
where $t_d(\bz; \bar{\bOmega}, \eta)$ is a $d$-dimensional Student's $t$-distribution with scale matrix $\bar{\bOmega}$ and degrees of freedom $\eta$, $Q(z) = \bz^T \bar{\Omega}^{-1}\bz$ and $T(\cdot; \eta)$ denotes the univariate Student's $t$ distribution function with $\eta$ degrees of freedom \citep{Azzalini2014}.

>>>>

% cross-referencing appendices
\usepackage{xr}
\externaldocument{skewt_rev}

% \usepackage[left=1in,top=1in,right=1in]{geometry}
% \pdfpageheight 11in
% \pdfpagewidth 8.5in
% \linespread{2.0}
\input{mycommands.sty}
\renewcommand{\fref}[1]{Web Figure~\ref{#1}}

@@

% \appendix
\renewcommand{\thesection}{Web Appendix~\Alph{section}}
% \renewcommand{\tablename}{Web Table}
% \renewcommand{\figurename}{Web Figure}
% \renewcommand{\thetable}{Web Table \arabic{table}}

\section{MCMC details} \label{sta:mcmc}
The MCMC sampling for the model in \sref{sts:hier} is done using {\tt R} (http://www.r-project.org). Whenever possible, we select conjugate priors (see \aref{sta:posterior}); however, for some of the parameters, no conjugate prior distributions exist.
For these parameters, we use a random walk Metropolis-Hastings update step.
In each Metropolis-Hastings update, we tune the algorithm during the burn-in period to give acceptance rates near 0.40.

\subsection*{Spatial knot locations}
For each day, we update the spatial knot locations, $\bw_1, \ldots, \bw_K$, using a Metropolis-Hastings block update.
Because the spatial domain is bounded, we generate candidate knots using the transformed knots $\bw^*_1, \ldots, \bw^*_K$ (see \sref{sts:temporal}) and a random walk bivariate Gaussian candidate distribution
\begin{align*}
	{\bw^*_k}^{(c)} \sim \text{N}({\bw^*_k}^{(r - 1)}, s^2 I_2)
\end{align*}
where ${\bw^*_k}^{(r - 1)}$ is the location for the transformed knot at MCMC iteration $r - 1$, $s$ is a tuning parameter, and $I_2$ is an identity matrix.
After candidates have been generated for all $K$ knots, the acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[ Y_t(\bs | \bw_1^{(c)}, \ldots, \bw_K^{(c)}, \ldots)] }{l[ Y_t(\bs | \bw_1^{(r - 1)}, \ldots, \bw_K^{(r - 1)}, \ldots)]} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K}\phi(\bw_k^{(c)})}{ \prod_{k = 1}^{K}\phi(\bw_k^{(r - 1)})} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K} p({\bw^*_k}^{(c)})}{ \prod_{k = 1}^{K} p({\bw^*_k}^{(r - 1)})}\right\}
\end{align*}
where $l$ is the likelihood given in \eref{steq:hier}, and $p(\cdot)$ is the prior either taken from the time series given in \eref{sts:temporal} or assumed to be uniform over $\calD$.
The candidate knots are accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial random effects}
If there is no temporal dependence amongst the observations, we use a Gibbs update for $z_{tk}$, and the posterior distribution is given in \aref{sta:posterior}.
If there is temporal dependence amongst the observations, then we update $z_{tk}$ using a Metropolis-Hastings update.
Because this model uses $|z_{tk}|$, we generate candidate random effects using the $z^*_{tk}$ (see \sref{sts:temporal}) and a random walk Gaussian candidate distribution
\begin{align*}
  {z^*_{tk}}^{(c)} \sim \text{N}({z^*_{tk}}^{(r - 1)}, s^2)
\end{align*}
where ${z^*_{tk}}^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
The acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[Y_t(\bs) | z_{tk}^{(c)}, \ldots] }{ l[Y_t(\bs) | z_{tk}^{(r - 1)}]} \right\} \times \left\{ \frac{ p[ z_{tk}^{(c)} ] }{ p[ z_{tk}^{(r - 1)}]}\right\}
\end{align*}
where $p[\cdot]$ is the prior taken from the time series given in \sref{sts:temporal}.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Variance terms}
When there is more than one site in a partition, then we update $\sigma^2_{tk}$ using a Metropolis-Hastings update.
First, we generate a candidate for $\sigma^2_{tk}$ using an IG$(a^*/s, b^*/s)$ candidate distribution in an independence Metropolis-Hastings update where $a^* = (n_{tk} + 1) / 2 + a$, $b^* = [Y_{tk}^\prime \Sigma^{-1}_{tk} Y_{tk} + z_{tk}^2] / 2 + b$, $n_{tk}$ is the number of sites in partition $k$ on day $t$, and $Y_{tk}$ and $\Sigma^{-1}_{tk}$ are the observations and precision matrix for partition $k$ on day $t$.
The acceptance ratio is
\begin{align*}
  R = \left\{
    \frac{ l[Y_t(\bs) | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[Y_t(\bs) | {\sigma^2_{tk}}^{(r - 1)}]}
    \right\} \times \left\{
    \frac{ l[z_{tk} | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[z_{tk} | {\sigma^2_{tk}}^{(r - 1)}, \ldots] }
    \right\} \times \left\{
    \frac{ p[ {\sigma^2_{tk}}^{(c)} ] }
         { p[ {\sigma^2_{tk}}^{(r - 1)}] }
    \right\} \times \left\{
    \frac{ c[ {\sigma^2_{tk}}^{(r - 1)}] }
         { c[ {\sigma^2_{tk}}^{(c)}]}
    \right\}
\end{align*}
where $p[\cdot]$ is the prior either taken from the time series given in \sref{sts:temporal} or assumed to be IG$(a, b)$, and $c[\cdot]$ is the candidate distribution.
The candidate is accepted with probability $\min\{R, 1\}$.

@@

\section{Posterior distributions} \label{sta:posterior}

\subsection*{Conditional posterior of $z_{tk} \mid \ldots $}\label{sts:mvcondu}
If knots are independent over days, then the conditional posterior distribution of $|z_{tk}|$ is conjugate.
For simplicity, drop the subscript $t$, let $\tilde{z}_{tk} = |z_{tk}|$, and define
\begin{align*}
R(\bs) = \left\{
    \begin{array}{ll}
        Y(\bs) - X(\bs) \beta &s \in P_l\\[1em]
        Y(\bs) - X(\bs) \beta - \lambda \tilde{z}(\bs) \qquad & s \notin P_l
    \end{array}
\right.
\end{align*}
Let
\begin{align*}
    R_1 &= \text{the vector of } R(\bs) \text{ for } s \in P_l \\
    R_2 &= \text{the vector of } R(\bs) \text{ for } s \notin P_l \\
    \Omega &= \Sigma^{-1}.
\end{align*}
Then
\begin{align*}
    \pi(z_l | \ldots) &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)^\prime
        \left( \begin{array}{cc}
            \Omega_{11} & \Omega_{12}\\
            \Omega_{21} & \Omega_{22}
        \end{array} \right)
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)
        +  \frac{ {\tilde{z}_l}^2 }{ \sigma_l^2 }\right]
    \right\} I(z_l > 0) \\
        &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \Lambda_l {\tilde{z}_l}^2 - 2 \mu_l \tilde{z}_l \right] \right\}
\end{align*}
where
\begin{align*}
    \mu_l &= \lambda ( R_1^\prime \Omega_{11} + R_2^\prime \Omega_{21} )\bOne\\
    \Lambda_l &= \lambda^2 \bOne^\prime \Omega_{11} \bOne + \frac{ 1 }{ \sigma^2_l }.
\end{align*}
Then $\tilde{Z}_l | \ldots \sim N_{(0, \infty)} (\Lambda_l^{-1} \mu_l, \Lambda_l^{-1})$

\subsection*{Conditional posterior of $\beta \mid \ldots$}\label{sts:betapost}
Let $\beta \sim \mbox{N}_{p}(0, \Lambda_0)$ where $\Lambda_0$ is a precision matrix. Then
\begin{align*}
    \pi(\beta \mid \ldots) & \propto \exp \left\{ - \frac{ 1 }{ 2 } \beta^\prime \Lambda_0 \beta - \frac{ 1 }{ 2 } \sum_{t = 1}^{n_t} [\bY_t - X_t \beta - \lambda |z_t|]^\prime \Omega [\bY_t - X_t \beta - \lambda |z_t|] \right\}\\
     & \propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \beta^\prime \Lambda_\beta \beta  - 2 \sum_{t = 1}^{n_t} [ \beta^\prime X_t^\prime \Omega (\bY_t - \lambda |z_t| )] \right] \right\}\\
     & \propto \mbox{N} ( \Lambda_\beta^{-1} \mu_\beta , \Lambda_\beta^{-1})
\end{align*}
where
\begin{align*}
    \mu_\beta &= \sum_{t = 1}^{n_t} \left[ X_t^\prime \Omega (\bY_t - \lambda |z_t|) \right]\\
    \Lambda_\beta &= \Lambda_0 + \sum_{t = 1}^{n_t} X_t^\prime \Omega X_t.
\end{align*}

\subsection*{Conditional posterior of $\sigma^2 \mid \ldots$}\label{sts:sigpost}
In the case where $L = 1$ and temporal dependence is negligible, then $\sigma^2$ has a conjugate posterior distribution.
Let $\sigma_t^2 \iid \mbox{IG}(\alpha_0, \beta_0)$. For simplicity, drop the subscript $t$. Then
\begin{align*}
    \pi(\sigma^2 \mid \ldots) & \propto (\sigma^2)^{ -\alpha_0 - 1 / 2 - n / 2 - 1} \exp \left\{ -\frac{\beta_0}{\sigma^2} - \frac{ |z|^2 }{2 \sigma^2} - \frac{ (\bY - \bmu)^\prime \Sigma^{-1} (\bY - \bmu) }{2 \sigma^2} \right\} \\
    & \propto (\sigma^2)^{ -\alpha_0 - 1 / 2 - n / 2 - 1} \exp \left\{ - \frac{ 1 }{ \sigma^2 } \left[\beta_0 + \frac{ |z|^2 }{ 2 } + \frac{ 1 }{ 2 } (\bY - \bmu)^\prime \Sigma^{-1} (\bY - \mu) \right] \right\} \\
    & \propto \mbox{IG} (\alpha^*, \beta^*)
\end{align*}
where
\begin{align*}
    \alpha^* &= \alpha_0 + \frac{1}{2} + \frac{n}{2} \\
    \beta^* &= \beta_0 + \frac{ |z|^2 }{ 2 } + \frac{ 1 }{ 2 }(\bY - \bmu)^\prime \Sigma^{-1} (\bY - \bmu).
\end{align*}
In the case that $L > 1$, a random walk Metropolis Hastings step will be used to update $\sigma^2_{lt}$.

\subsection*{Conditional posterior of $\lambda \mid \ldots$}\label{sts:lambdapost}
\hl{TODO: Still needs to be updated for single $\lambda$}\\
For convergence purposes we model $\lambda = \lambda_1 \lambda_2$ where
\begin{align}
  \lambda_1 &= \left\{ \begin{array}{ll}
      +1 \quad & \text{w.p.} 0.5\\
      -1 \quad & \text{w.p.} 0.5
   \end{array}\right.\\
   \lambda^2_2 & \sim IG(\alpha_\lambda, \beta_\lambda).\\
\end{align}
Then
\begin{align*}
  \pi(\lambda_2 \mid \ldots) &\propto {\lambda_2^2}^{(-\alpha_\lambda - 1)} \exp\left\{ - \frac{ \beta_\lambda }{ \lambda_2^2} \right\} \prod_{t = 1}^{n_t} \prod_{k = 1}^K \frac{1} {\lambda_2} \exp\left\{ - \frac{ z^2_{tk} }{ 2 \lambda_2^2  \sigma_{tk})^2} \right\} \\
   & \propto {\lambda_2^2}^{(-\alpha_\lambda - K*n_t - 1)} \exp \left\{ -\frac{1}{\lambda^2_2} \left[ \beta_\lambda + \frac{ z^2 }{2 \sigma^2_{tk}} \right] \right\}
\end{align*}
Then $\lambda_2 \mid \ldots \sim IG \left(\alpha_\lambda + K * n_t, \beta_\lambda + \frac{ z^2 }{2 \sigma^2_{tk}} \right)$

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{sta:proofsamepartition}
Let $c$ be the midpoint of $\bs_1$ and $\bs_2$.
Define $A$ as the circle centered at $c$ with radius $h / 2$ where $h = ||\bs_1 - \bs_2||$ is the distance between sites $\bs_1$ and $\bs_2$.
Consider a homogeneous spatial Poisson process over $A$ with intensity given by
\begin{align*}
  \mu_{PP}(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PPA}^* h^2.
\end{align*}
Consider a partition of $A$ into four regions, $B_1$, $B_2$, $R_1$, $R_2$ as seen in \fref{stfig:hpp}.
\begin{figure}
  \includegraphics[width=\linewidth]{plots/circles}
  \caption{Illustration of the partition of $A$.}
  \label{stfig:hpp}
\end{figure}
Let $N_i$ be the number of knots in $B_i$ and $L_i = l$ if $\bs_i \in P_l$ for $i = 1, 2$.
Then
\begin{align}
  P(L_1 \neq L_2) \ge P(N_1 > 0, N_2 > 0)
\end{align}
since knots in both $B_1$ and $B_2$ is sufficient, but not necessary, to ensure that $\bs_1$ and $\bs_2$ are in different partition sets.
By definition of a Poission process, $N_1$ and $N_2$ are independent and thus $P(N_1 > 0, N_2 > 0) = P(N_1 > 0)^2$, and the intensity measure over $B_1$ is given by
\begin{align}
  \mu_{PP}(B_1) &= \lambda_{PP} |B_1| = \lambda_{PP} \frac{h^2}{4} \left(\frac{2 \pi}{3} - \frac{\sqrt{3}}{2} \right) \nonumber \\
       &= \lambda^*_{PPB1} h^2.
\end{align}
So,
\begin{align}
  P(L_1 \neq L_2) >= P(N_1 > 0)^2 = [1 - P(N_1 = 0)]^2 = [1 - \exp\left(-\lambda^*_{PPB1} h^2\right)]^2
\end{align}
which goes to 1 as $h$ goes to infinity.

@@

\section{Skew-$t$ distribution} \label{sta:skewt}
\subsection*{Univariate skew-$t$ distribution}
We say that $Y$ follows a univariate extended skew-$t$ distribution with location $\xi \in \calR$, scale $\omega > 0$, skew parameter $\alpha \in \calR$, and degrees of freedom $\nu$ if has distribution function
\begin{align}
  f_{\text{EST}}(y) = 2 f_T (z; \nu) F_T\left[ \alpha z \sqrt{ \frac{ \nu + 1 }{ \nu + z^2}}; \nu + 1 \right]
\end{align}
where $f_T(t; \nu)$ is a univariate Student's $t$ with $\nu$ degrees of freedom, $F_T(t; \nu) = P(T < t)$, and \hbox{$z = (y - \xi) / \omega$}.

\subsection*{Multivariate skew-$t$ distribution}
If $\bZ \sim \text{ST}_d(0, \bar{\bOmega}, \balpha, \eta)$ is a $d$-dimensional skew-$t$ distribution, and $\bY = \xi + \bomega \bZ$, where $\bomega = \text{diag}(\omega_1, \ldots, \omega_d)$, then the density of $Y$ at $y$ is
\begin{align}
  f_y(\by) = det(\bomega)^{-1} f_z(\bz)
\end{align}
where
\begin{align}
  f_z(\bz) &= 2 t_d(\bz; \bar{\bOmega}, \eta) T \left[ \balpha^\prime \bz \sqrt{ \frac{\eta + d}{\nu + Q(\bz)} }; \eta + d\right] \\
  \bz &= \bomega^{-1}(\by - \xi)
\end{align}
where $t_d(\bz; \bar{\bOmega}, \eta)$ is a $d$-dimensional Student's $t$-distribution with scale matrix $\bar{\bOmega}$ and degrees of freedom $\eta$, $Q(z) = \bz^\prime \bar{\Omega}^{-1}\bz$ and $T(\cdot; \eta)$ denotes the univariate Student's $t$ distribution function with $\eta$ degrees of freedom \citep{Azzalini2014}.

\subsection*{Extremal dependence}
For a bivariate skew-$t$ random variable $\bY = [Y(\bs), Y(\bt)]^\prime$, the $\chi(h)$ statistic \citep{Padoan2011} is given by
\begin{align} \label{steq:chiskew-t}
  \chi(h) = \bar{F}_{\text{EST}}\left\{ \frac{[x_1^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{\sqrt{1 - \varrho(h)^2}}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \frac{ [x_2^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{ \sqrt{1 - \varrho(h)^2} }; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\},
\end{align}
where $\bar{F}_{\text{EST}}$ is the univariate survival extended skew-$t$ function with zero location and unit scale, \hbox{$\varrho(h) = \text{cor}[y(\bs), y(\bt)]$}, $\alpha_j = \alpha_i \sqrt{1 - \varrho^2}$, $\tau_j = \sqrt{\eta + 1}(\alpha_j + \alpha_i \varrho)$, and $x_j = F_T(\bar{\alpha}_i \sqrt{\eta + 1}; 0, 1, \eta) / F_T(\bar{\alpha}_j \sqrt{\eta + 1}; 0, 1, \eta)$ with $j = 1, 2$ and $i = 2, 1$ and where $\bar{\alpha}_j = (\alpha_j + \alpha_i \varrho) / \sqrt{ 1 + \alpha_i^2 [1 - \varrho(h)^2]}$.
